Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference

### 2019-12-25 paper/paper.tex
paper

\hypersetup{
            pdftitle={Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference with crowdsourcing?},
            pdfkeywords={statistics, visual inference, geospatial, population},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison
using visual inference with crowdsourcing?}

@@

Geo-spatial statistics are often presented on the geographic map base.
To present geo-spatial population statistics, information for
individuals within each geographic region are often aggregated. A
choropleth map is the common display to present aggreagated statistics
for geographic units, and they are often used to present statistics
regarding the population. This visualisation method involves drawing the
administrative boundaries and filling them with colour to communicate
the value of the statistic. In Australia, there are many sets of
administrative boundaries that define subdivisions of the population at
various granularities.

When presenting population statistics on a geographic map base, the size
of the regions can allow errornous conclusions to be drawn about the
state of the statistic over the entire population. This occurs as large
regions filled with a consistent colour or pettern can draw the
attention of map readers, and small regions are not paid equal
attention.

\hypertarget{background-and-motivation}{%
\section{Background and Motivation}\label{background-and-motivation}}

@@

\begin{itemize}
\tightlist
\item
  Communicating spatial distributions
\item
  Trend over geographic space
\item
  Trend over communities and populations
\end{itemize}

The Australian Cancer Atlas explores the burden of cancer on Australian
communities. There are many cancer types presented, and they can be
explored on an individual or aggregate level. The Australian communities
examined are Statistical Areas at Level 2 (SA2)(``Australian Statistical
Geography Standard (ASGS)'' 2018) used by the Australian Bureau of
Statistics. Bayesian spatial smoothing has been applied to incorporate
the statistics of neighbouring areas, for both privacy and stability of
the estimates. The statistics that can be mapped are the diagnoses
(Standardised Incidence Rates) and excess deaths for each SA2,
communicated as the difference from the Australian average of the
statistics. The values of the statistic for each are communicated using
a diverging colour scheme. Dark blue represents areas with values much
less than the Australian average, and represents areas much greater than
the Australian average.

\begin{itemize}
\tightlist
\item
  Communicating data through visualisations
\item
  Effective displays for types of data
\item
  Testing the effectiveness
\end{itemize}

Classical statistical inferences involves hypothesis testing, the
process of rejecting a null hypothesis in favour of an alternative. This
approach relies on data, the appropriate distributions and their
assumptions.

\hypertarget{line-up-protocol}{%
\subsection{Line up protocol}\label{line-up-protocol}}

The lineup protocol presents a method for visual inference testing.

\begin{quote}
``In this framework, plots take on the role of test statistics, and
human cognition the role of statistical tests.'' Buja et al. (2009)
\end{quote}

The lineup protocol can be used in a variety of tsting scenarios. The
choropleth map is best used for testing spatial structure in a data set.

@@

@@

\hypertarget{aims}{%
\subsection{Aims}\label{aims}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are spatial disease trends, that impact highly populated small areas,
  detected with higher accuracy when viewed in a hexagon tile map
  display?
\item
  Are people faster in detecting spatial disease trends, that impact
  highly populated small areas, when using a hexagon tile map display?
\item
  Do people find hexagon tile maps more difficult to read than
  choropleth maps?
\item
  Are the reasons for choosing a plot different depending on the type of
  display?
\item
  Does an Australian resident find the choropleth map easier to read
  than the hexagon tile map?
\end{enumerate}

A survey was created to test the effectiveness of the hexagon tile map
display.

The online crowdsource platform Figure-Eight was used to recruit
participants. A line up protocol was implemented to arrange 12 maps in
each display. Individual displays were created by a combination of plot
type, and spatial trend model.

@@

The researchers compared the length of time taken, and the accuracy of
the participants choices.

\hypertarget{the-participants}{%
\subsection{The participants}\label{the-participants}}

There were 95 participants in the study. We recruited participants using
the Figure-Eight crowd source platform by advertising this survey to
participants that fulfilled the following crtieria:

• level 2 or level 3 on the Figure-Eight Platform. • at least 18 years
old

@@

\hypertarget{the-variables-being-manipulated-and-measured}{%
\subsection{The variables being manipulated and
measured?}\label{the-variables-being-manipulated-and-measured}}

Each participant was randomly allocated to either group A or group B
when they begun the survey. This resulted in 42 participants allocated
to group A, and 53 participants allocated to group B.

The levels of the factors measured in the experiment were: • Plot type:
\emph{Geography, Hexagons} • Trend: \emph{Locations in two population
centres, Locations in multiple population centres, South-East to
North-West}

Factor combinations examined by each participant amount to 6 (2x3)
lineup displays. A participant did see the same data for both plot
types. Four simulated sets of data were generated for each treatment.
This will generate 24 lineups (12 were geographic maps, and 12 were
hexagon tile maps). Participants will evaluate 12 lineups, 6 of each
plot type. Appendix A shows the experimental design visually. For each
of the six geographic displays and six hexagon displays, two of each
trend model were shown to participants.

\hypertarget{participant-training}{%
\subsection{Participant training}\label{participant-training}}

Each participant saw three test displays orienting them to the task.
Participants proceeded to the survey, this involved evaluating 12
displays.

@@

The participant submitted demographic questions and provided consent
before evaluating the lineups.

Demographics were collected regarding the study participants: • Gender
(female / male / other), • Degree education level achieved (high school
/ bachelors / masters / doctorate / other), • Age range (18-24 / 25-34 /
35-44 / 45-54 / 55+ / other) • Lived at least for one year in Australia
(Yes / No )

Participants then moved to the evaulation phase. The set of images
differed for group A and group B. After being allocated each individual
was shown the 12 displays in randomised order.

@@

Data was collected through a web application containing the online
survey. Each participant used the internet to access the survey.

The data collection took place using a secure link between the survey
web application and the googlesheet used to store results. The
application would first connect to the googlesheet using the
googlesheets (Bryan and Zhao 2018) R package, and interacted again at
the completion of the survey by adding the participant's responses to
the 12 displays as 12 rows of data in the googlesheet.

@@

The data analysis methods used in order to analyse and collate the
results included downloading the survey submissions and opening them
into the analysis software R ({\textbf{???}}).

For each of the 12 lineup displays the researchers calculated: •
accuracy: the proportion of subjects who detected the data plot •
efficiency: average time taken to respond

@@

Side-by-side dot plots were made of accuracy (efficiency) against plot
type, facetted by trend model type.

@@

The results will be analysed using a generalised linear model, with a
subject random effect. There will be two main effects: plot type and
trend model, which gives the fixed effects part of the model to be

@@

where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the plot type effect,
\(\delta_j\) is the trend model effect. We are allowing for an
interaction between plot type and trend model. Because the response is
binary, a logistic model is used.

@@

Computation will be done using R ({\textbf{???}}), with the
\texttt{lme4} package ({\textbf{???}}).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Type\\
\item
  Trend
\item
  Interaction of type and trend
\item
  Demographics of participants
\end{enumerate}

The survey responses from participants were kept only if the participant
submitted answers for all 12 displays. This resulted in 95 surveyed.

\includegraphics{survey_files/figure-latex/unnamed-chunk-2-1.pdf}

\includegraphics{survey_files/figure-latex/unnamed-chunk-4-1.pdf}

\begin{verbatim}
## # A tibble: 2 x 2
##   gender     n
##   <chr>  <int>
## 1 He        70
## 2 She       25
\end{verbatim}

\begin{verbatim}
## # A tibble: 6 x 2
##   age         n
##   <chr>   <int>
## 1 18 - 24    15
## 2 25 - 34    37
## 3 35 - 44    23
## 4 45 - 54    11
## 5 55+         6
## 6 NA          3
\end{verbatim}

\begin{verbatim}
## # A tibble: 3 x 2
##   education       n
##   <chr>       <int>
## 1 Bach           56
## 2 High School    25
## 3 Masters        14
\end{verbatim}

\begin{verbatim}
## # A tibble: 2 x 2
##   australia     n
##   <chr>     <int>
## 1 No           93
## 2 Yes           2
\end{verbatim}

\includegraphics{survey_files/figure-latex/unnamed-chunk-7-1.pdf} 11 of
the 12 real distribution plots were found more often in the hexagon
display. This was better than expected. As even geographic distributions
were spotted in the hexagon lineup.

\includegraphics{survey_files/figure-latex/unnamed-chunk-8-1.pdf}

\begin{verbatim}
## [1] 0.004079185
\end{verbatim}

\includegraphics{survey_files/figure-latex/unnamed-chunk-9-1.pdf}
\includegraphics{survey_files/figure-latex/unnamed-chunk-9-2.pdf}

\includegraphics{survey_files/figure-latex/unnamed-chunk-10-1.pdf}
\includegraphics{survey_files/figure-latex/unnamed-chunk-10-2.pdf}

\includegraphics{survey_files/figure-latex/unnamed-chunk-11-1.pdf}

\hypertarget{probability-of-detection}{%
\subsection{Probability of detection:}\label{probability-of-detection}}

\hypertarget{time-taken}{%
\subsection{Time taken}\label{time-taken}}

\hypertarget{modeling-1}{%
\subsection{Modeling}\label{modeling-1}}

@@

The conclusion goes here.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-abs2016}{}%
``Australian Statistical Geography Standard (ASGS).'' 2018.
\emph{Australian Bureau of Statistics}. Australian Government.
\url{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}.

@@

>>>>

\hypersetup{
            pdftitle={Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference},
            pdfkeywords={statistics, visual inference, geospatial, population},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison
using visual inference}

@@

Geospatial statistics are often presented on the geographic map base. A
choropleth map is the common display to present aggreagated statistics
for geographic units, and they are often used to present statistics
regarding the population. Creating a choropleth map involves drawing the
administrative boundaries and filling them with colour to communicate
the value of the statistic. In Australia, there are sets of
administrative boundaries that define subdivisions of the population at
various granularities. The set of Australia statistical areas presents
an example of a heterogrenous distribution of area. The rural
communicates on a much larger geographic space than small inner city
communities. This has the negative effect of incorrectly showing the
spatial distribution of the statistic, especially when a spatial
distribution is related to the size of the areas, or the population
density.

An alternative display can also be used to effectively communicate a
spatial distribution for a set of heterogeneous areas. Viewers of
spatial distributions may come to incorrect conclusions.

\hypertarget{motivation}{%
\section{Motivation}\label{motivation}}

@@

The Australian Cancer Atlas explores the burden of cancer on Australian
communities. There are many cancer types presented, and they can be
explored on an individual or aggregate level. The Australian communities
are examined at the Statistical Areas at Level 2 (SA2)(``Australian
Statistical Geography Standard (ASGS)''
\protect\hyperlink{ref-abs2016}{2018}) used by the Australian Bureau of
Statistics. Bayesian spatial smoothing has been applied to incorporate
the statistics of neighbouring areas, for both privacy and stability of
the estimates. The statistics that can be mapped are the diagnoses
(Standardised Incidence Rates) and excess deaths for each SA2,
communicated as the difference from the Australian average of the
statistics. The values of the statistic for each are communicated using
a diverging colour scheme.

The Australian Cancer Atlas communicates the trends in the distributions
of cancer over geographic space. It uses a choropleth map display and
diverging colour scheme to draw attention to relationships between
neighbouring areas.

\hypertarget{background}{%
\section{Background}\label{background}}

Spatial visualisations - Choropleth However, the issue of using a
choropleth map base becomes obvious when considering the distributions.
Position is extremely important for analysis of a visualisation.

@@

When presenting population statistics on a geographic map base, the size
of the regions can allow errornous conclusions to be drawn about the
state of the statistic over the entire population. This occurs as large
regions filled with a consistent colour or pettern can draw the
attention of map readers, and small regions are not paid equal
attention. A choropleth map is not the only display that can be used for
presenting geospatial data. Alternative maps include various cartograms,
and tesselated tile maps. They allow other variables to be included in
the display to highlight the staistical values of various geographic
areas.

\begin{itemize}
\tightlist
\item
  Communicating data through visualisations
\item
  Effective displays for types of data
\item
  Protocol for testing the effectiveness
\end{itemize}

Classical statistical inference involves hypothesis testing, the process
of rejecting a null hypothesis in favour of an alternative. This
approach relies on data, the appropriate distributions and their
assumptions. Visual inference null hypothesis: independence in the
variables (absence of all features), alternative hypothesis:
Relationship between the variables (presence of some feature).

The lineup protocol is used for visual inference testing. 1. simulate
null plots 2. Insert data with structure into a random location 3. Ask
uninvolved person to select the most different plot 4. If location is
chosen correctly, the existence of a feature is significant at
\(\alpha = 1/N\).

\begin{quote}
``In this framework, plots take on the role of test statistics, and
human cognition the role of statistical tests.'' Buja et al.
(\protect\hyperlink{ref-SIEDAMD}{2009})
\end{quote}

The lineup protocol can be used in a variety of testing scenarios. The
choropleth map is best used for testing spatial structure in a data set.

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are spatial disease trends, that impact highly populated small areas,
  detected with higher accuracy when viewed in a hexagon tile map
  display?
\item
  Are people faster in detecting spatial disease trends, that impact
  highly populated small areas, when using a hexagon tile map display?
\end{enumerate}

additional considerations when completing this experimental task
included exploration of the difficulty experienced by participants

\hypertarget{experimental-design}{%
\subsection{Experimental design}\label{experimental-design}}

The most common display for spatial cancer data is the choropleth map.
This will be the comparative visualisation for presenting the lineups
(Majumder, Hofmann, and Cook \protect\hyperlink{ref-VVSIALM}{2013}).
Most geographic distributions will have some degree of spatial
autcorrelation between neighbours. This feature will exist in all plots
in the lineup displays, the plot that contains the trend feature shown
in only one set of data will also be affected by spatial
autocorrelation. A reasonable amount of null plots \(N-1\) in the lineup
was chosen to ensure data is well hidden. For the detailed choropleth of
Australian SA2 areas, we set \(N = 12\) to not overwhelm participants. A
line up protocol was implemented to arrange 12 maps in each display.
Individual displays were created by a combination of map type, and
spatial trend model.

The hypotheses for each lineup are \(H_0\) : All plots look the same
\(H_a\) : One plot looks different to the other plots

Recruited participants to be uninvolved judges with no prior knowledge
of the data to avoid discrimination or advantages. The online
crowdsource platform Figure-Eight was used to recruit participants.

@@

Let \(n\) be the number of independent observers and \(x_i\) the number
of observers who picked plot \(i\), \(i = \{1,...,m\}\)

Then \(x_i, x_2, ..., x_m\) follows a multinomial
distribution\(Mult_{\pi_1, \pi_2, ...., \pi_m}(x_i, x_2, ..., x_m)\)
with \(\sum_i \pi_i = 1\), where \(\pi_i\) is the probability that plot
\(i\) is picked by an observer, which we can estimate as
\(\hat{\pi}_i = x_i/n\). The researchers compared the length of time
taken, and the accuracy of the participants choices. The power of a
lineup can therefore be estimated as the ratio of correct
identifications \(x\) out of \(n\) viewings.

\hypertarget{the-variables-being-manipulated-and-measured}{%
\subsection{The variables being manipulated and
measured}\label{the-variables-being-manipulated-and-measured}}

Each participant was randomly allocated to either Group A or Group B
when they begun the survey. This resulted in 42 participants allocated
to Group A, and 53 participants allocated to Group B.

The levels of the factors measured in the experiment were: - Map type:
\emph{Choropleth, Hexagon tile} - Trend: \emph{Locations in three
population centres, Locations in multiple population centres, South-East
to North-West}

Factor combinations examined by each participant amount to 6 (2x3)
lineup displays. A participant did see the same data for both map types.
Four simulated sets of data were generated for each treatment. This will
generate 24 lineups (12 were geographic maps, and 12 were hexagon tile
maps). Participants will evaluate 12 lineups, 6 of each map type.
Appendix A shows the experimental design visually. For each of the six
geographic displays and six hexagon displays, two of each trend model
were shown to participants.

\begin{table}[]
\caption{The Experimental Design}
\label{tab:my-table}
\begin{tabular}{|l|l|l|}
\hline
Trend & Map type & Replicates \\ \hline
NW-SE & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
Three cities & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
All cities & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
\end{tabular}
\end{table}

\hypertarget{simulation-process}{%
\subsection{Simulation process}\label{simulation-process}}

The underlying spatial correlation model was created to provide spatial
autocorrelation between neighbouring areas using the longitude and
latitude values for the Statistical Areas. formula = z \textasciitilde{}
1, locations = \textasciitilde{} longitude + latitude

Simulated spatially dependent data using the model on the centroids of
each area, for 12 null plots in 12 lineups.

12 sets of data were created. In these 12 sets of data, each of the 144
maps were smoothed several times to replicate the spatial
autocorrelation seen in cancer data sets presented in the Australian
Cancer Atlas.

For each of the 144 individual maps, the values attributed to each
geographic area are rescaled to show a similar colour scale from deep
blue to dark red within each map.

A random location was selected for each set of lineup data. In this
location, a trend model was overlaid on the null set of spatially
correlated data. Each set of lineup data was used to produce a
choropleth maps and hexagon tile maps. These matched pairs were split
between Group A and Group B.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

There were 95 participants involved in the study. We recruited
participants using the Figure-Eight crowd source platform by advertising
this survey to participants that fulfilled the following crtieria:

\begin{itemize}
\tightlist
\item
  level 2 or level 3 on the Figure-Eight Platform.
\item
  at least 18 years old
\end{itemize}

@@

Each participant was trained using three test displays orienting them to
the evaluation task. Participants then proceeded to the survey, this
involved evaluating 12 displays.

@@

The participant answered demographic questions and provided consent
before evaluating the lineups.

Demographics were collected regarding the study participants: - Gender
(female / male / other), - Degree education level achieved (high school
/ bachelors / masters / doctorate / other), - Age range (18-24 / 25-34 /
35-44 / 45-54 / 55+ / other) - Lived at least for one year in Australia
(Yes / No )

Participants then moved to the evaulation phase. The set of images
differed for Group A and Group B. After being allocated to a group, each
individual was shown the 12 displays in randomised order.

@@

Data was collected through a web application containing the online
survey. Each participant used the internet to access the survey. The
data collection took place using a secure link between the survey web
application and the googlesheet used to store results. The application
would first connect to the googlesheet using the googlesheets (Bryan and
Zhao \protect\hyperlink{ref-sheets}{2018}) R package, and interacted
again at the completion of the survey by adding the participant's
responses to the 12 displays as 12 rows of data in the googlesheet.

@@

The data analysis methods used in order to analyse and collate the
results included downloading the survey submissions and opening them
into the analysis software R (R Core Team
\protect\hyperlink{ref-RCore}{2019}).

For each of the 12 lineup displays the researchers calculated: -
accuracy: the proportion of subjects who detected the data plot -
efficiency: average time taken to respond

@@

Side-by-side dot plots were made of accuracy (efficiency) against map
type, facetted by trend model type.

@@

The results will be analysed using a generalised linear model, with a
subject random effect to account for differences in individuals. There
will be two main effects: map type and trend model, which gives the
fixed effects part of the model to be

@@

where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
\(\delta_j\) is the trend model effect. We are allowing for an
interaction between map type and trend model. Because the response is
binary, a logistic model is used.

@@

Computation will be done using R (R Core Team
\protect\hyperlink{ref-RCore}{2019}), with the \texttt{lme4} package
(Bates et al. \protect\hyperlink{ref-lme4}{2015}).

@@

The survey responses from participants were kept only if the participant
submitted answers for all 12 displays. This resulted in 95 participants.

The contributors who detected no plots correctly were analysed further.
Three of these contribuotrs gave no choices for any of the twelve
displays. They were also removed for the rest of the analysis. The
contributors who gave various plot choices and reasons for the twelve
displays were kept.

\hypertarget{demographics}{%
\subsection{Demographics:}\label{demographics}}

\begin{verbatim}
## # A tibble: 6 x 2
##   age     participants
##   <chr>          <int>
## 1 18 - 24           14
## 2 25 - 34           37
## 3 35 - 44           21
## 4 45 - 54           11
## 5 55+                6
## 6 NA                 3
\end{verbatim}

\begin{tabular}{l|r|r|r|r}
\hline
Gender & Bach & High School & Masters & Row Total\\
\hline
Col. Total & 56 & 23 & 13 & 79\\
\hline
He & 39 & 19 & 9 & 58\\
\hline
She & 17 & 4 & 4 & 21\\
\hline
\end{tabular}

70 of the 95 participants were male, and 25 female and only two of the
participants had lived in Australia before.

70 of the participants achieved a Bachelors or Masters degree.

\hypertarget{accuracy}{%
\section{Accuracy}\label{accuracy}}

The detection rate is used to find the accuracy for participants
reporting the real data trend model. The accuracy can be seen from many
views.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
\caption{Each point shows the probability of detection for the lineup
display, separated by the trend model hidden in the lineup. The points
for the same data set are linked to show the difference in the detection
rate when the same data was seen in each display. 11 of the 12 real
distribution plots were found more often in the hexagon display.}
\end{figure}

\begin{tabular}{l|l|r|r|r}
\hline
trend & type & replicate & mean & std.dev\\
\hline
NW-SE & Choropleth & 1 & 25.00 & 16.41\\
\hline
NW-SE & Choropleth & 2 & 21.12 & 15.28\\
\hline
NW-SE & Choropleth & 3 & 21.12 & 17.05\\
\hline
NW-SE & Choropleth & 4 & 21.20 & 14.52\\
\hline
NW-SE & Hexagon tiles & 1 & 19.53 & 14.56\\
\hline
NW-SE & Hexagon tiles & 2 & 21.95 & 16.42\\
\hline
NW-SE & Hexagon tiles & 3 & 22.02 & 16.12\\
\hline
NW-SE & Hexagon tiles & 4 & 18.17 & 14.51\\
\hline
three cities & Choropleth & 1 & 15.30 & 13.88\\
\hline
three cities & Choropleth & 2 & 25.22 & 14.36\\
\hline
three cities & Choropleth & 3 & 22.49 & 15.87\\
\hline
three cities & Choropleth & 4 & 18.68 & 13.74\\
\hline
three cities & Hexagon tiles & 1 & 20.37 & 17.02\\
\hline
three cities & Hexagon tiles & 2 & 19.95 & 16.59\\
\hline
three cities & Hexagon tiles & 3 & 20.02 & 17.19\\
\hline
three cities & Hexagon tiles & 4 & 18.02 & 16.93\\
\hline
all cities & Choropleth & 1 & 20.14 & 16.56\\
\hline
all cities & Choropleth & 2 & 22.75 & 14.72\\
\hline
all cities & Choropleth & 3 & 19.88 & 15.03\\
\hline
all cities & Choropleth & 4 & 19.33 & 16.15\\
\hline
all cities & Hexagon tiles & 1 & 19.83 & 15.87\\
\hline
all cities & Hexagon tiles & 2 & 16.96 & 14.65\\
\hline
all cities & Hexagon tiles & 3 & 19.21 & 15.27\\
\hline
all cities & Hexagon tiles & 4 & 20.03 & 15.11\\
\hline
\end{tabular}

A t-test shows the difference between the detection rates for the two
types of displays. The value of 0.0041593 shows that it is very unlikely
the difference is due to chance.

\hypertarget{speed}{%
\subsection{Speed}\label{speed}}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/time-1.pdf}
\caption{The time taken to evaluate each display is broken into five
second windows. The height of the histogram bars show how many
evaulations were submitted within each time window. The distributions
for the choropleth and hexagon tile maps are very similar. Both have a
large peak at 0-5 seconds, and then a secondary peak at 10-20 seconds.
No response took over one minute.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/time_compare-1.pdf}
\caption{Each point shows the average time taken for participants to
evalute the lineup display, separated by the trend model hidden in the
lineup. The points for the same data set are linked to show the
difference in the avergae time taken when the same data was seen in each
display. There is a lot of variation in the time taken. The shortest
average time (15 seconds), and the longest average time (23 seconds)
both occured when evaluating three cities}
\end{figure}

\hypertarget{certainty}{%
\subsection{Certainty}\label{certainty}}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{The amount of times each level of certainty was chosen by
participants when viewing hexagon tile map or choropleth displays.
Participants were more likely to choose a high certainty when
considering a Choropleth map. The default certainty of 3 was chosen most
for the Hexagon tile map displays.}
\end{figure}

Certainty levels are measured on a five point scale---they are
subjective assessments by the participant `how certain are you about
your choice?'.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{The amount of times each level of certainty was chosen by
participants. The columns shown whether a viewer correctly selected the
real trend data plot when viewing hexagon tile map or choropleth
displays.}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{The amount of times each level of certainty was chosen by
participants. The columns shown whether a viewer correctly selected the
real trend data plot when viewing hexagon tile map or choropleth
displays. The rows show the type of the trend model added in the real
data plot. The default certainty level of 3 was chosen most frequently
when incorrect. Then shown a NW-SE or all cities trend participants felt
more certain of their correct choice.}
\end{figure}

\hypertarget{reason}{%
\subsection{Reason}\label{reason}}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{The most common reason for choice of plot when looking at each
trend model shown in Choropleth and Hexagon Tile maps. Clusters were the
most common reason when viewing a Hexagon Tile map, trend was the most
common choice for choropleth displays except for the all cities
display.}
\end{figure}

\hypertarget{contributors}{%
\subsection{Contributors}\label{contributors}}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{The probablity of detection acheived by the contributors in
each group is shown by the points. Group B has a larger range and a
smaller inter-quartile range. Group A and both had 3 people who did not
find any of the data maps in the displays.}
\end{figure}

\hypertarget{reason-1}{%
\subsection{Reason}\label{reason-1}}

\includegraphics{paper_files/figure-latex/unnamed-chunk-6-1.pdf}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/choices-1.pdf}
\caption{Each facet is associated with one lineup, the height of the
bars count the choices made by the participants considering each lineup.
The bars coloured with black outlines show the map which contained a
trend model, these are the correct choices. The numbers differentiate
the replicates of each trend model and type of map display. Participants
were able to select 0 to indicate they did not want to choose a map.}
\end{figure}

The choices made by participants are examined in Figure
\ref{fig:choices}. Participants were misled by the choropleth display,
but not the hexagon display for all cities displays except (2). The maps
with a North West to South East trend was chosen with much greater
frequency in all displays. All of three cities displays, except (4),
were detected in the hexagon display. All except one lineup had at least
one participant select the correct map in the lineup as shown in Figure
\ref{fig:choices}.

\hypertarget{anomolies}{%
\subsection{Anomolies}\label{anomolies}}

\hypertarget{modeling-the-difference}{%
\subsection{Modeling the difference}\label{modeling-the-difference}}

A generalized linear mixed effects model can account for each individual
participants' abilities as it includes a subject-specific random
intercept. As each participant provides results from 12 lineups.

\hypertarget{detection-rates}{%
\subsubsection{Detection Rates}\label{detection-rates}}

\begin{verbatim}
## # A tibble: 6 x 5
##   term                                estimate std.error statistic p.value
##   <chr>                                  <dbl>     <dbl>     <dbl>   <dbl>
## 1 (Intercept)                           0.0217     0.147     0.147   0.883
## 2 typeHexagon tiles                     0.420      0.211     1.99    0.047
## 3 trendthree cities                    -3.25       0.412    -7.88    0    
## 4 trendall cities                      -1.24       0.229    -5.41    0    
## 5 typeHexagon tiles:trendthree cities   2.37       0.465     5.10    0    
## 6 typeHexagon tiles:trendall cities     1.08       0.312     3.47    0.001
\end{verbatim}

\begin{verbatim}
## Analysis of Deviance Table
## 
## Model: binomial, link: logit
## 
## Response: detect_f
## 
## Terms added sequentially (first to last)
## 
## 
##            Df Deviance Resid. Df Resid. Dev  Pr(>Chi)    
## NULL                        1103     1477.0              
## type        1   83.526      1102     1393.5 < 2.2e-16 ***
## trend       2  101.699      1100     1291.8 < 2.2e-16 ***
## type:trend  2   35.517      1098     1256.2 1.939e-08 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{verbatim}
##            
##             Incorrect Correct
##   Incorrect       431     121
##   Correct         242     310
\end{verbatim}

\begin{verbatim}
## # A tibble: 1 x 6
##   sigma logLik   AIC   BIC deviance df.residual
##   <dbl>  <dbl> <dbl> <dbl>    <dbl>       <int>
## 1 0.430  -675. 1367. 1407.    1321.        1096
\end{verbatim}

\begin{verbatim}
## # A tibble: 8 x 5
##   term                                estimate std.error statistic group      
##   <chr>                                  <dbl>     <dbl>     <dbl> <chr>      
## 1 (Intercept)                            0.505    0.0340     14.9  fixed      
## 2 typeHexagon tiles                      0.103    0.0448      2.31 fixed      
## 3 trendthree cities                     -0.467    0.0448    -10.4  fixed      
## 4 trendall cities                       -0.277    0.0448     -6.19 fixed      
## 5 typeHexagon tiles:trendthree cities    0.250    0.0633      3.95 fixed      
## 6 typeHexagon tiles:trendall cities      0.239    0.0633      3.77 fixed      
## 7 sd_(Intercept).contributor             0.118   NA          NA    contributor
## 8 sd_Observation.Residual                0.430   NA          NA    Residual
\end{verbatim}

\begin{verbatim}
##            
##             Incorrect Correct
##   Incorrect        49       1
##   Correct         624     430
\end{verbatim}

For a base model of Choropleth map, using a NW-SE trend model. The
detection rate for Hexagon tile maps using a NW-SE trend model changes
the log odds of the detection by 0.42.

\hypertarget{certainty-1}{%
\subsubsection{Certainty}\label{certainty-1}}

\begin{verbatim}
## Linear mixed model fit by REML ['lmerMod']
## Formula: detect ~ type * trend + (1 | contributor)
##    Data: d
## REML criterion at convergence: 1350.719
## Random effects:
##  Groups      Name        Std.Dev.
##  contributor (Intercept) 0.1179  
##  Residual                0.4296  
## Number of obs: 1104, groups:  contributor, 92
## Fixed Effects:
##                         (Intercept)                    typeHexagon tiles  
##                              0.5054                               0.1033  
##                   trendthree cities                      trendall cities  
##                             -0.4674                              -0.2772  
## typeHexagon tiles:trendthree cities    typeHexagon tiles:trendall cities  
##                              0.2500                               0.2391
\end{verbatim}

@@

how do the results found generalise to other work - Not just for Aus
(Canada new Zealand could also use this effective display)

\begin{itemize}
\tightlist
\item
  For USA alternative methods can also be helpful
\end{itemize}

\hypertarget{supplementary-materials}{%
\section{Supplementary Materials}\label{supplementary-materials}}

\hypertarget{training}{%
\subsection{Training}\label{training}}

\hypertarget{survey-application}{%
\subsection{Survey application}\label{survey-application}}

\hypertarget{subject-specific-anomolies-0-detection}{%
\subsection{Subject specific anomolies (0\%
detection)}\label{subject-specific-anomolies-0-detection}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-abs2016}{}%
``Australian Statistical Geography Standard (ASGS).'' 2018.
\emph{Australian Bureau of Statistics}. Australian Government.
\href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{\{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian   Statistical Geography Standard (ASGS)\}}.

\leavevmode\hypertarget{ref-lme4}{}%
Bates, Douglas, Martin Mächler, Ben Bolker, and Steve Walker. 2015.
``Fitting Linear Mixed-Effects Models Using lme4.'' \emph{Journal of
Statistical Software} 67 (1): 1--48.
\url{https://doi.org/10.18637/jss.v067.i01}.

@@

\leavevmode\hypertarget{ref-VVSIALM}{}%
Majumder, Mahbubul, Heike Hofmann, and Dianne Cook. 2013. ``Validation
of Visual Statistical Inference, Applied to Linear Models.''
\emph{Journal of the American Statistical Association} 108 (503):
942--56. \url{https://doi.org/10.1080/01621459.2013.808157}.

\leavevmode\hypertarget{ref-RCore}{}%
R Core Team. 2019. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.
